The 2018 heatwave and its implications on ozone induced damage on vegetation in a subarctic climate

### 2020-04-24 VegOzone.tex
Cosmetix.

Ozone concentrations \chem{[O_3]} measured in $2\,\unit{m}$ height above ground are averaged hourly. As can be seen in Fig.~\ref{fig:data_svanvik_2018_2019}a), \chem{[O_3]} peaks in spring (April/May) and reaches its minimum in late summer (July/August). The spring peak has not been captured completely in 2019, for data acquisition started later than in 2018. In summer 2018 (June--August), high ozone concentrations ($\chem{[O_3]} > 40\,\unit{ppb}$) were recorded 50 times. The highest summer ozone concentration ($\chem{[O_3]} = 50.2\,\unit{ppb}$) was measured on July 25. This coincides with the period of the most extensive forest fires in central Swedish (G\"{a}vleborgs, J\"{a}mtlands, and Dalarnas l\"{a}n) which occurred from July 12--29 and destroyed about $18000\,\unit{hectare}$ of forest{\bf TODO: Cite chapter 11 Swedish government report.}. {\bf TODO: Do we need a corresponding \chem{CO_2} emission here?} However, due to the above mentioned data acquisition problems, we miss most of the corresponding ozone data for this event and most likely also the peak ozone concentration. In contrast, ozone concentration only rose 18 times above the threshold of $40\,\unit{ppb}$ during the summer of 2019.

>>>>

Ozone concentrations \chem{[O_3]} measured in $2\,\unit{m}$ height above ground are averaged hourly. As can be seen in Fig.~\ref{fig:data_svanvik_2018_2019}a), \chem{[O_3]} peaks in spring (April/May) and reaches its minimum in late summer (July/August). The spring peak has not been captured completely in 2019, for data acquisition started later than in 2018. In summer 2018 (June--August), high ozone concentrations ($\chem{[O_3]} > 40\,\unit{ppb}$) were recorded 50 times. The highest summer ozone concentration ($\chem{[O_3]} = 50.2\,\unit{ppb}$) was measured on July 25. This coincides with the period of the most extensive forest fires in central Swedish (G\"{a}vleborgs, J\"{a}mtlands, and Dalarnas l\"{a}n) which occurred from July 12--29 and destroyed about $18000\,\unit{hectare}$ of forest{\bf TODO: Cite chapter 11 Swedish government report.}. {\bf TODO: Do we need a corresponding \chem{CO_2} emission here?} However, due to the above mentioned data acquisition problems, we missed most of the corresponding ozone data for this event and most likely also the peak ozone concentration. In contrast, ozone concentration only rose 18 times above the threshold of $40\,\unit{ppb}$ during the summer of 2019.
